Figures to insert in text

### 2018-04-09 Chapters/Chapter0A.tex
closing for the day...

Finally, how long does it take for a dissertation to be completed? The time is either less than or equal to the duration allowed by the Grad College for the completion of a Ph.D or it is greater. In the latter case, infinite number of petitions can be filed for extensions. Since the Grad College never remembers previous petitions, the total number of petitions received by the Grad College is always one, a small constant\footnote{`With apologies to non-CS types': this wonderful result is from Bala Rajagopalan, posted on the late rec.humor.funny Usenet in June 12 1989.}.

>>>>

Finally, how long does it take for a dissertation to be completed? The time is either less than or equal to the duration allowed by the Grad College for the completion of a Ph.D or it is greater. In the latter case, infinite number of petitions can be filed for extensions. Since the Grad College never remembers previous petitions, the total number of petitions received by the Grad College is always one, a small constant\footnote{`With apologies to non-CS types': this seminal, wonderful, result is from Bala Rajagopalan, published on the late rec.humor.funny Usenet in June 12, 1989.}.

### 2018-04-09 Chapters/Conclusion.tex
closing for the day...

With this, I submit this thesis in the hope that all readers, present and future, may find the aforementioned studies as useful, genuine, and legitimate contributions to the thriving field of Computational Management Science.

>>>>

With this, I submit this thesis in the hope that all readers, present and future, may find the aforementioned studies as useful, genuine, and legitimate contributions to the thriving field of Computational Management Science\footnote{Finally, for the skeptical reader that may argue against the decision towards `arbitrary technical reports on unrelated topics', a reference to the ``fundamental research theorem'', reprinted in Appendix \ref{Recent Results in Theory of Computing - I}, seems, of course, virtually inescapable.}.

### 2018-04-09 Chapters/Introduction.tex
closing for the day...

A second and final qualification: It is my hope that readers of this thesis will accept the format of self-contained studies, as just as valid as a monograph on a particular topic\footnote{e.g., the ``fundamental research theorem'' in the Appendix}.  With these qualifications, we are ready to venture into the world of computational management science.

>>>>

A second and final qualification: It is my hope that readers of this thesis will accept the format of self-contained studies, as just as valid as a monograph on a particular topic.  With these qualifications, we are ready to venture into the world of computational management science.
